---
title: "User Avatar Bond Discrepancy Questionnaire"
author: "Taylor Brown"
date: '2022-04-06'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#First step: Cleaning the Data

Step 1: Install and Run Packages
```{r setup, include=FALSE}
#options(scipen = 999)
options(max.print=1000000)
install.packages("tidyverse")
install.packages("haven")
install.packages("mlmi")
install.packages("mice")
install.packages("VIM")
install.packages("knitr")
install.packages("psych")

#Run packages

library(tidyverse)
library(haven) #if you used it once - you don't have to load the whole library just reference in code as haven::read_sav
library(mlmi) #for ml imputations
library(mice) #an alternative to mlmi
library(VIM)#visualization and imputation of missing values
library(knitr)
library(psych)

knitr::opts_chunk$set(echo = TRUE)
```
Import Data
```{r}
df <- haven::read_sav("alldatarev.sav") %>%
  mutate_all(~replace(., . == 99, NA))
#View(DF) - better option is to do 
df%>%head()
knitr::kable(describe(df), caption = "Descriptive stats", digits = 2)

```
Examine the Data
```{r}
df%>%select(contains("Dis"))%>%
  skimr::skim()%>%
  knitr::kable() #optional but make it look nicer in the html output
#summary(df[ , grepl("Dis", colnames(df))])
```
Visualization of Missing Values
```{r}
df%>%select(contains("Dis"))%>%
VIM::aggr(numbers = TRUE)
knitr::kable() 
```


Removal of %missing
```{r}
#Participants (rows) with more than a 10% of missing values need to be deleted. 
#option 1: more step-by-step and easy to digest
df<-df%>%
  mutate(
    NA_percent=rowMeans(
      is.na(
        #change contains to whichever var you want to use including range df[, 44-59]
        select(df, contains("Dis"))
        )
      )
  )%>%
  filter(
    NA_percent<0.3
    )%>%
  select(-NA_percent)
```

renaming mahalanobis to final
```{r}
final_data<-df
```

Skew and Kurtosis
```{r}
#change the below from df to final_data if you want to use data without outliers
final_data%>%
  select(contains("Dis"))%>%
  moments::skewness(na.rm=TRUE)
final_data%>%
  select(contains("Dis"))%>%
  moments::kurtosis(na.rm=TRUE)
```

MLE 5 Imputations for any remaining missing Val
```{r}
#missingness patterns
set.seed(1234)
final_data%>%
  select(contains("Dis"))%>%
  mice::md.pattern(rotate.names=TRUE)
final_data_imp<-final_data%>%
  select(contains("Dis"))%>%
  mice::mice(m=5)
#
final_data_imp
skimr::skim(final_data)
```
export data file
```{r}
write_sav(final_data, "TaylorCleaned.sav")
```


#EFA completed via Jamovi - Next step is CFA

First - install CFA & EFA packages with Lavaan & Lavaan Plot
```{r}
install.packages("lavaan")
install.packages("lavaanPlot")
install.packages("semTools")
install.packages("semPlot")
```

Second - run packages
```{r}
library (lavaan)
library(lavaanPlot)
library (semPlot)
library(semTools)
```

Third - import the dataset and define model

Specify the different models
```{r}
onefactormodel <- "useravatar =~ W2_Dis1 + W2_Dis2 + W2_Dis6 + W2_Dis7 + W2_Dis8Rev + W2_Dis9 + W2_Dis10Rev + W2_Dis15Rev"
```

Fourth - fit the model

Fit the model and save the results
```{r}
fit1 <- cfa(onefactormodel, data = CFA_Data, estimator= "DWLS")


summary(fit1, fit.measures=TRUE, standardized=TRUE)
```

Saved the table for fit 1
```{r}
tableformat1<-summary(fit1, fit.measures=TRUE, standardized=TRUE) 

modificationindices(fit1, sort. = TRUE)

```

Get Omega reliability for factors using 'semTools' package

```{r}

reliability(fit1, omit.imps = c("no.conv", "no.se"))


```

Graph the model
```{r}
lavaanPlot(model = fit1, edge_options = list(color = "grey"))

lavaanPlot(model = fit1, node_options = list(shape = "box", fontname = "Helvetica"), edge_options = list(color = "grey"), coef = FALSE)
```

Repeat procedure with the model but with a different estimator (ML)

```{r}
Fit2 <- cfa(onefactormodel, data = CFA_Data, estimator = "MLM")

summary(Fit2, fit.measures=TRUE, standardized=TRUE)

tableformat2<-summary(Fit2, fit.measures=TRUE, standardized=TRUE)

modificationindices(Fit2, sort. = TRUE)

reliability(Fit2, omit.imps = c("no.conv", "no.se"))

lavaanPlot(model = Fit2, node_options = list(shape = "box", fontname = "Helvetica"), edge_options = list(color = "grey"), coef = FALSE)
```

Repeat again with same model but with a different estimator (WLS)

```{r}
fit3 <- cfa(onefactormodel, data = CFA_Data, estimator = "WLS")

summary(fit3, fit.measures=TRUE, standardized=TRUE)

tableformat3<-summary(fit3, fit.measures=TRUE, standardized=TRUE)

modificationindices(fit3, sort. = TRUE)

reliability(fit3, omit.imps = c("no.conv", "no.se"))

```

#Now we have a confirmed model we will conduct an IRT


Load packages
```{r}
library(mirt)
library(naniar)
library(Rcpp)

```

Define data
```{r}
data<-haven::read_sav("IRT_Data.sav")%>%
  mutate_if(is.character, as.factor)

```


view data and define the scale
```{r}
glimpse(data)

scale <-(data[,2:9])

head(scale, 8) 

```

Fit the graded response model using the 'mirt' R package.
```{r}

mod1 <- (mirt(scale, 1, verbose = FALSE, itemtype = 'graded', SE = TRUE))

M2(mod1, type = "C2", calcNull = FALSE, na.rm = TRUE)

```

Check missing values
```{r}

naniar::mcar_test(scale)

```
This value is well below the recommended threshold of 5% (Schafer, 1999).

A Little’s missing completely at random (MCAR) test showed that all missing values were missing completely at random.

Examine items fit

```{r}

itemfit(mod1, na.rm = TRUE)

```

Examine IRT parameters 
(0 = non discriminative; 0.01–0.34 = very low; 0.35–0.64 = low; 0.65–1.34 = moderate; 1.35–1.69 = high; >1.70 = very high; Baker, 2001)

```{r}

IRT_parms <- coef(mod1, IRTpars = TRUE, simplify = TRUE, na.rm=TRUE)
IRT_parms$items

```

Examine Factor analysis parameters

```{r}

summary(mod1)

```

Produce IRT plots - Category characteristic Curve

```{r plot1, echo=FALSE}

plot(mod1, type='trace', which.item = c(1,2,3,4,5,6,7,8), facet_items=T, 
     as.table = TRUE, auto.key=list(points=F, lines=T, columns=4, space = 'top', cex = .8), 
     theta_lim = c(-3, 3), 
     main = "")


```


Item information Curve

```{r plot2, echo=FALSE}

plot(mod1, type='infotrace', which.item = c(1,2,3,4,5,6,7,8), facet_items=T, 
     as.table = TRUE, auto.key=list(points=F, lines=T, columns=1, space = 'right', cex = .8), 
     theta_lim = c(-3, 3), 
     main="")

```

Scale informaiton and conditional standard errors

```{r plot3, echo=FALSE}

plot(mod1, type = 'infoSE', theta_lim = c(-3, 3), 
     main="")

```

Conditional reliability

```{r plot4, echo=FALSE}

plot(mod1, type = 'rxx', theta_lim = c(-3, 3), 
     main="" )

## Single IRT reliability is also produced ##

marginal_rxx(mod1)


```

Scale characteristic Curve


```{r plot5, echo=FALSE}

plot(mod1, type = 'score', theta_lim = c(-3, 3), main = "")

```

# THE END



